Cover Letter: Cudele (Paper 306)

### 2018-02-28 paper/sections/3_posix_overheads.tex
paper: typos, reviewer comments, and  deltafs clarifications
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\textbf{Comparison to decoupled namespaces}: For BatchFS, if a client fails
when it is writing to the local log-structured merge tree (implemented as an
SSTable~\cite{ren:atc2013-tablefs}) then unwritten metadata operations are
lost. For DeltaFS, if the client fails then, on restart, the computation does
the work again -- since the snapshots of the namespace are never globally
consistent and there is no ground truth.  On the server side, BatchFS and
DeltaFS use IndexFS~\cite{ren:sc2014-indexfs}. IndexFS writes metadata to
SSTables, which initially reside in memory but are later flushed to the
underlying distributed file system.

>>>>

\textbf{Comparison to decoupled namespaces}: For BatchFS and DeltaFS, if the
client fails and stays down then computation must be done again because the
metadata updates were never globally consistent.  Both systems write metadata
to log-structured merge trees (implemented as
SSTables~\cite{ren:atc2013-tablefs}) so updates initially reside in memory but
are later flushed to the underlying file system. As a result, after a client
crash, updates that have not been written safely to disk may be lost.  On the
server side, BatchFS and DeltaFS use IndexFS~\cite{ren:sc2014-indexfs}.
IndexFS writes metadata to SSTables as well but writes to lower tiers are
globally persisted in a distributed file system.

### 2018-02-28 paper/sections/6_results.tex
paper: typos, reviewer comments, and  deltafs clarifications
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\newcomment{\indent We graph standard deviations for three runs (sometimes
error bars are too small to see) and normalize results to make our results more
generally applicable to different hardware. We use a CloudLab cluster of 34
nodes connected with 10Gbit ethernet, each with 16 2.4 GHz CPUs, 128GB RAM, and
400GB SSDs.  Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel
release, version 10.2.1, which was released in May 2016. We use 1 monitor
daemon, 3 object storage daemons, 1 metadata server daemon, and up to 20
clients.}  We scope the evaluation to one metadata server and scale the number
of parallel clients \newcomment{each doing 100K operations because 100K is the
maximum recommended size of a directory in CephFS. We scale to 20 clients
because, as shown in Section~\S\ref{sec:posix-overheads}, 20 clients is enough
to saturate the resources of a single metadata server.} This type of analysis
shows the capacity and performance of a metadata server with superior metadata
protocols, which should be used to inform \oldcomment{load
balancing}\newcomment{metadata distribution} across a \oldcomment{metadata}
cluster. Load balancing across a cluster of metadata servers with partitioning
and replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.  \newcomment{To make our results
reproducible, this paper adheres to The Popper
Convention~\cite{jimenez:ipdpsw17-popper} so experiments can be examined in more
detail, or even re-run, by visiting the \texttt{[source]} link next to each
figure.  The source code for Cudele is available on a branch~\cite{docs:cudele}
of our Ceph fork.}

@@

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark}; Big Data Benchmark jobs examined
in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens or
creates just to start a single Spark query and the Lustre system they tested on
did not handle creates well, showing up to a \(24\times\) slowdown compared to
other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system, like BatchFS or DeltaFS, that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}

@@

\newcomment{ ``Decoupled: merge + create" outperforms ``RPCs" by \(3.37\times\)
because ``decoupled: merge + create" uses a relaxed form of consistency and
leverages bulk updates just like DeltaFS~\cite{zheng:pdsw2015-deltafs}.
Decoupled namespaces (1)} place no restrictions on the validity of metadata
inserted into the journal ({\it e.g.}, never checking for the existence of
files before creating files), \newcomment{(2)} avoid touching poorly scaling
data structures\newcomment{, and (3) allow clients to batch events into bulk
updates}. \oldcomment{We can scale linearly if we weaken our consistency by
never checking for the existence of files before creating files ({\it i.e.}
only append \texttt{open()} requests to the journal).  When the updates are
merged by the metadata server into the in-memory metadata store they never scan
growing data structures.}  Had we implemented the \oldcomment{Append Client
Journal mechanism}\newcomment{client to send updates one at a time and} to
include \texttt{lookup()} commands before \texttt{open()} requests, we would
have seen \newcomment{performance closer to the ``RPC" subtree}\oldcomment{the
poor scaling that we see with the RPCs mechanism}. \newcomment{The ``decoupled:
merge + create" curve is also pessimistic because it models a scenario in which
all client journals arrive at the same time.} So for the 20 clients data point,
we are measuring the operations per second for 20 client journals that land on
the metadata server at the same time. \newcomment{Had we added infrastructure
to overlay journal arrivals or time client sync intervals, we could have
scaled more closely to ``decoupled: create".}\oldcomment{The ``create + merge"
bar adds the time it takes for clients to generate the journal of events in
parallel. ALSO DISCUSS 3.7X!!}

>>>>

\newcomment{\indent We graph standard deviations for three runs (sometimes
error bars are too small to see) and normalize results to make our results more
generally applicable to different hardware. We use a CloudLab cluster of 34
nodes connected with 10Gbit ethernet, each with 2 2.4 GHz CPUs (16 total cores), 128GB RAM, and
400GB SSDs.  Each node uses Ubuntu 14.04 and we develop on Ceph's Jewel
release, version 10.2.1, which was released in May 2016. We use 1 monitor
daemon, 3 object storage daemons, 1 metadata server daemon, and up to 20
clients.}  We scope the evaluation to one metadata server and scale the number
of parallel clients \newcomment{each doing 100K operations because 100K is the
maximum recommended size of a directory in CephFS. We scale to 20 clients
because, as shown in Section~\S\ref{sec:posix-overheads}, 20 clients is enough
to saturate the resources of a single metadata server.} This type of analysis
shows the capacity and performance of a metadata server with superior metadata
protocols, which should be used to inform \oldcomment{load
balancing}\newcomment{metadata distribution} across a \oldcomment{metadata}
cluster. Load balancing across a cluster of metadata servers with partitioning
and replication can be explored with something like
Mantle~\cite{sevilla:sc15-mantle}.  \newcomment{To make our results
reproducible, this paper adheres to The Popper
Convention~\cite{jimenez:ipdpsw17-popper} so experiments can be examined in more
detail, or even re-run, by visiting the \texttt{[source]} link next to each
figure.  The source code for Cudele is available on a branch~\cite{docs:cudele}
of our Ceph fork.}

@@

\oldcomment{Next we show how we can build application-specific subtrees by
composing mechanisms and that this approach of coupling well-established
techniques to specific applications results in a more a scalable global
namespace.} We start with clients creating files in private directories because
this workload is heavily studied in HPC~\cite{weil:sc2004-dyn-metadata,
ren:sc2014-indexfs, patil:fast2011-giga, zheng:pdsw2014-batchfs,
sevilla:sc15-mantle}, mostly due to checkpoint-restart~\cite{bent_plfs_2009}.
A more familiar example is uncompressing an archive ({\it e.g.}, \texttt{tar
xzf}), where the file system services a flash crowd of creates across all
directories as shown in Figure~\ref{fig:overhead-creates}.  But the workload
also appears in cloud workloads: Hadoop/Spark use the file \newcomment{system
to assign work units to workers and the performance is proportional to the
open/create throughput of the underlying file system~\cite{xiao:socc15-shardfs,
shi:vldb15-spark}; Big Data Benchmark jobs examined
in~\cite{chaimov:hpdc16-spark} have on the order of 15,000 file opens or
creates just to start a single Spark query and the Lustre system they tested on
did not handle creates well, showing up to a \(24\times\) slowdown compared to
other metadata operations. Common approaches to solve these types of
bottlenecks is to change the application behavior or to design a new file
system that uses one set of metadata optimizations
for the entire namespace.} \oldcomment{ abstraction to exchange work units to
workers or to indicate when jobs complete  The workload is clients creating
100K files in private directories in the same global namespace.}

@@

\newcomment{ ``Decoupled: merge + create" outperforms ``RPCs" by \(3.37\times\)
because ``decoupled: merge + create" uses a relaxed form of consistency and
leverages bulk updates just like DeltaFS.
Decoupled namespaces (1)} place no restrictions on the validity of metadata
inserted into the journal ({\it e.g.}, never checking for the existence of
files before creating files), \newcomment{(2)} avoid touching poorly scaling
data structures\newcomment{, and (3) allow clients to batch events into bulk
updates}. \oldcomment{We can scale linearly if we weaken our consistency by
never checking for the existence of files before creating files ({\it i.e.}
only append \texttt{open()} requests to the journal).  When the updates are
merged by the metadata server into the in-memory metadata store they never scan
growing data structures.}  Had we implemented the \oldcomment{Append Client
Journal mechanism}\newcomment{client to send updates one at a time and} to
include \texttt{lookup()} commands before \texttt{open()} requests, we would
have seen \newcomment{performance closer to the ``RPC" subtree}\oldcomment{the
poor scaling that we see with the RPCs mechanism}. \newcomment{The ``decoupled:
merge + create" curve is also pessimistic because it models a scenario in which
all client journals arrive at the same time.} So for the 20 clients data point,
we are measuring the operations per second for 20 client journals that land on
the metadata server at the same time. \newcomment{Had we added infrastructure
to overlay journal arrivals or time client sync intervals, we could have
scaled more closely to ``decoupled: create".}\oldcomment{The ``create + merge"
bar adds the time it takes for clients to generate the journal of events in
parallel. ALSO DISCUSS 3.7X!!}
